Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-08-07 tex/ms.tex
add a Tests subsection with some things to do.  cleanup figure captions for new color scheme

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Spectra resulting from draws from the posterior parameter
space conditioned on the calibrated \excluster~ spectrum and
photometry.  Left: For each of 5 draws from the posterior we show from
top to bottom, three components of the model: the mean cluster
spectrum, the calibration vector, and the mean prediction of $\Delta$
for the Gaussian process.  Right: From top to bottom, the full model
({\it cyan}) compared to the observed, calibrated spectrum ({\it
magenta}), the ratio of the observed to the modeled spectrum, and the
difference between the observed spectrum and the modeled spectrum
normalized by the uncertainty.
\label{fig:inferred_spectrum}}
\end{figure*}

@@

@@

>>>>

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Spectra resulting from draws from the posterior parameter
space conditioned on the calibrated \excluster~ spectrum and
photometry.  Left: For each of 5 draws from the posterior we show from
top to bottom, three components of the model: the mean cluster
spectrum, the calibration vector, and the mean prediction of $\Delta$
for the Gaussian process.  Right: From top to bottom, the full model
({\it magenta}) compared to the observed, calibrated spectrum ({\it
grey}), the ratio of the observed to the modeled spectrum, and the
difference between the observed spectrum and the modeled spectrum
normalized by the uncertainty.
\label{fig:inferred_spectrum}}
\end{figure*}

@@

\subsection{Tests}

@@

BDJ: Then, we infer the parameters of the calibrated spectrum without
including the noise model!  What changed, what did we get wrong
without the noise model?

BDJ: We should also test on fake data
